A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-06-09 paper/paper.tex
inserted north graph evaluation.

>>>>

\section{Experiments on the North Graph Testset}

\todo[inline]{Say something about north graph}

\begin{figure}[htb]
\centering
\subfloat[\label{fig:northCrossing-1}{Crossing resolution vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================
% Crossing Resolution
%======================
\begin{tikzpicture}
\begin{axis}[
axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,
legend style={at={(0.425,1.35)},anchor=north,,legend columns=2,draw=none},
width=0.475\textwidth,
cycle list name=mylist, 
mark repeat={5},xlabel={Number of Vertices},ylabel={Crossing Resolution},
xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={10,20,30,40,50,60,70,80,90},
tick pos=left,ymajorgrids]
\addplot table [x=avg, y=cr rm, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=cr rm-1, col sep=semicolon] {crossingResolutionNorth.csv};
\addplot table [x=avg, y=cr fa, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=cr tr, col sep=semicolon] {crossingResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northCrossing-2}{Aspect ratio vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%===================================
% Crossing Resolution Aspect Ratio
%===================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none},ylabel style={yshift=-0.2cm}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={0,10,20,30,40,50,60,70,80,90,100},ylabel={Aspect Ratio},
xlabel={Number of Vertices},
xmin=10,
xmax=100,
ytick={1,2,5,10,20,50,100,200},ymode=log, log ticks with fixed point,tick pos=left, ymajorgrids,]
\addplot table [x=avg, y=ar rm, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=ar rm-1, col sep=semicolon] {crossingResolutionNorth.csv};
\addplot table [x=avg, y=ar fa, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=ar tr, col sep=semicolon] {crossingResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}

\subfloat[\label{fig:northCrossing-3}{No.~of crossings vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================================
% Crossing Resolution Crossing Number
%======================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist,  mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,250,500,750,1000,1250,1500,1750},ylabel={Number of Crossings},
xlabel={Number of Vertices},tick pos=left,ylabel style={yshift=-0.2cm}, ymajorgrids]
\addplot table [x=avg, y=cn rm, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=cn rm-1, col sep=semicolon] {crossingResolutionNorth.csv};
\addplot table [x=avg, y=cn fa, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=cn tr, col sep=semicolon] {crossingResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northCrossing-4}{Iterations vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%==================================
% Crossing Resolution Iterations
%==================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,1000,2000,3000,4000,5000,6000,7000,8000},tick pos=left, 
ylabel={Iterations},
xlabel={Number of Vertices},ymajorgrids]
\addplot table [x=avg, y=it rm, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=it rm-1, col sep=semicolon] {crossingResolutionNorth.csv};
\addplot table [x=avg, y=it fa, col sep=semicolon]{crossingResolutionNorth.csv};
\addplot table [x=avg, y=it tr, col sep=semicolon] {crossingResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\caption{Experimental results for the crossing resolution experiment on the North graph testset.}
\label{northCrossing}
\end{figure}

\begin{figure}[htb]
\centering
\subfloat[\label{fig:northTotal-1}{Total resolution vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================
% Total Resolution
%======================
\begin{tikzpicture}
\begin{axis}[
axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,
legend style={at={(0.425,1.35)},anchor=north,,legend columns=2,draw=none},
width=0.475\textwidth,
cycle list name=mylist, 
mark repeat={5},xlabel={Number of Vertices},ylabel={Total Resolution},
xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={10,20,30,40,50,60,70,80,90},
tick pos=left,ymajorgrids]
\addplot table [x=avg, y=tr rm, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=tr rm-1, col sep=semicolon] {totalResolutionNorth.csv};
\addplot table [x=avg, y=tr fa, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=tr tr, col sep=semicolon] {totalResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northTotal-2}{Aspect ratio vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%===================================
% Total Resolution Aspect Ratio
%===================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none},ylabel style={yshift=-0.2cm}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={0,10,20,30,40,50,60,70,80,90,100},ylabel={Aspect Ratio},
xlabel={Number of Vertices},
xmin=10,
xmax=100,
ytick={1,2,5,10,20,50,100,200},ymode=log, log ticks with fixed point,tick pos=left, ymajorgrids,]
\addplot table [x=avg, y=ar rm, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=ar rm-1, col sep=semicolon] {totalResolutionNorth.csv};
\addplot table [x=avg, y=ar fa, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=ar tr, col sep=semicolon] {totalResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}

\subfloat[\label{fig:northTotal-3}{No.~of crossings vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================================
% Total Resolution Crossing Number
%======================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist,  mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,250,500,750,1000,1250,1500,1750},ylabel={Number of Crossings},
xlabel={Number of Vertices},tick pos=left,ylabel style={yshift=-0.2cm}, ymajorgrids]
\addplot table [x=avg, y=cn rm, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=cn rm-1, col sep=semicolon] {totalResolutionNorth.csv};
\addplot table [x=avg, y=cn fa, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=cn tr, col sep=semicolon] {totalResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northTotal-4}{Iterations vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%==================================
% Total Resolution Iterations
%==================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,1000,2000,3000,4000,5000,6000,7000,8000},tick pos=left, 
ylabel={Iterations},
xlabel={Number of Vertices},ymajorgrids]
\addplot table [x=avg, y=it rm, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=it rm-1, col sep=semicolon] {totalResolutionNorth.csv};
\addplot table [x=avg, y=it fa, col sep=semicolon]{totalResolutionNorth.csv};
\addplot table [x=avg, y=it tr, col sep=semicolon] {totalResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\caption{Experimental results for the total resolution experiment on the North graph testset.}
\label{northTotal}
\end{figure}

\begin{figure}[htb]
\centering
\subfloat[\label{fig:northAngular-1}{Angular resolution vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================
% Angular Resolution
%======================
\begin{tikzpicture}
\begin{axis}[
axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,
legend style={at={(0.425,1.35)},anchor=north,,legend columns=2,draw=none},
width=0.475\textwidth,
cycle list name=mylist, 
mark repeat={5},xlabel={Number of Vertices},ylabel={Angular Resolution},
xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={10,20,30,40,50,60,70,80,90},
tick pos=left,ymajorgrids]
\addplot table [x=avg, y=an rm, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=an rm-1, col sep=semicolon] {angularResolutionNorth.csv};
\addplot table [x=avg, y=an fa, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=an tr, col sep=semicolon] {angularResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northAngular-2}{Aspect ratio vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%===================================
% Angular Resolution Aspect Ratio
%===================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none},ylabel style={yshift=-0.2cm}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={0,10,20,30,40,50,60,70,80,90,100},ylabel={Aspect Ratio},
xlabel={Number of Vertices},
xmin=10,
xmax=100,
ytick={1,2,5,10,20,50,100,200},ymode=log, log ticks with fixed point,tick pos=left, ymajorgrids,]
\addplot table [x=avg, y=ar rm, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=ar rm-1, col sep=semicolon] {angularResolutionNorth.csv};
\addplot table [x=avg, y=ar fa, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=ar tr, col sep=semicolon] {angularResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}

\subfloat[\label{fig:northAngular-3}{No.~of crossings vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%======================================
% Angular Resolution Crossing Number
%======================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist,  mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,250,500,750,1000,1250,1500,1750},ylabel={Number of Crossings},
xlabel={Number of Vertices},tick pos=left,ylabel style={yshift=-0.2cm}, ymajorgrids]
\addplot table [x=avg, y=cn rm, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=cn rm-1, col sep=semicolon] {angularResolutionNorth.csv};
\addplot table [x=avg, y=cn fa, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=cn tr, col sep=semicolon] {angularResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\subfloat[\label{fig:northAngular-4}{Iterations vs no.~of vertices}]{
\centering
\scalebox{.95}{
\centering
%==================================
% Angular Resolution Iterations
%==================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},ylabel style={yshift=-0.2cm},axis y line*=left,legend style={at={(0.425,1.35)},
anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mylist, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},
xmin=10,
xmax=100,
ytick={0,1000,2000,3000,4000,5000,6000,7000,8000},tick pos=left, 
ylabel={Iterations},
xlabel={Number of Vertices},ymajorgrids]
\addplot table [x=avg, y=it rm, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=it rm-1, col sep=semicolon] {angularResolutionNorth.csv};
\addplot table [x=avg, y=it fa, col sep=semicolon]{angularResolutionNorth.csv};
\addplot table [x=avg, y=it tr, col sep=semicolon] {angularResolutionNorth.csv};
\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}}
\caption{Experimental results for the angular resolution experiment on the North graph testset.}
\label{northAngular}
\end{figure}
